Transfer learning for echelle spectroscopy

### 2021-11-15 paper/paper1/ms.tex
start the results section, some placeholder text

\begin{outline}
  \1 We compute the residual of native PHOENIX minus cloned model
  \1 We see X percent residuals at native resolution
  \1 We smooth the residual to HPF instrumental resolution and see Y percent residuals
  \1 The main residuals come from missing line opacity due to our prominence threshold:
  \1 Including smaller prominence lines means smaller residuals, but more lines and higher computational cost
\end{outline}

\subsection{Line data clustering and conspicuous flaws}
\begin{outline}
  \1 We see some lines that devolve into missing continuum opacity
  \1 Especially acute near broad line wings if you don't handle the non-standard line shapes
  \1 How do the lineshapes cluster in $\sigma_G$ vs $FWHM_L$?
  \1 How do the lineshapes cluster in Amplitude vs FWHM? Can some lines be rejected?
  \1 Does the pre-trained model round-trip effectively (model saved at end of training = model from loaded params)?
\end{outline}

>>>>

We compute the residual $\mathsf{R}(\bm{\lambda}_s)$ of native PHOENIX minus cloned model, illustrated in the bottom panel of Figure XX\authorcomment1{make this figure}.  We see an RMS of $\blackout{1}\%$ residuals at native resolution, with a long tail of residuals up to $\blackout{20}\%$.  The greatest residuals surround the deepest and broadest lines---such as Hydrogen and neutral alkali metal lines---for which the non-Voigt lineshapes stand out.  Figure ZZ\authorcomment1{make this figure} zooms in on the XX\authorcomment1{todo} line at $\censor{10200}\;$\AA.

The other main source of large residuals is simply missing line opacity due to our finite prominence threshold.  Lines with prominence less than $P_{rom}$ yield residuals that scale with $P_{rom}$.  Including smaller prominence lines means smaller residuals, but more lines and higher computational cost.

\subsection{Line data clustering and conspicuous flaws}
We see some narrow lines devolve into missing continuum opacity, the favored tradeoff when the continuum estimate's poor performance outweighs the the pain of a narrow-but-tolerably-small spike.  This problem can be seen in Figure XX where a line initialized at $\censor{10210}\;$\AA~ with an amplitude of ZZ and width of YY bloats to \censor{some other value}.  These devolved lines tend to appear poorly immitated line wings.  One can mitigate these devolved lines by adding more flexibility to the continuum or supporting more advanced line shapes.

\begin{outline}
  \1 We see some lines that devolve into missing continuum opacity
  \1 How do the lineshapes cluster in $\sigma_G$ vs $FWHM_L$?
  \1 How do the lineshapes cluster in Amplitude vs FWHM? Can some lines be rejected?
  \1 Does the pre-trained model round-trip effectively (model saved at end of training = model from loaded params)?
\end{outline}
